Mainstreaming Race Science

### 2023-10-23 paper/paper.Rmd
just do acknowledgments manually

acknowledgements: |
  | Thanks to Emily Merchant and John Jackson for some initial discussions that helped clarify the scope of the project and identify some key resources related to the Pioneer Fund and *Mankind Quarterly*.  Thanks to Anthony Sainez for help retrieving the *Mankind Quarterly* articles.  Thanks to Derek Devnich and James Dooley for their work attempting to secure the APA-published articles.  Thanks to Kevin Bird, John Jackson, and Manuela Fernández Pinto for comments on a draft of this paper. 
  | **Funding:** EJCL's work on this project was partially supported by UC Merced.  DJH's work on this project was not supported by any specific funding. 
  | **Author contributions:** DJH (conceptualization, data curation, formal analysis, investigation, methodology, project administration, software, validation, visualization, writing-original draft, writing-review & editing); EJCL (conceptualization, methodology, software, validation, visualization, writing-original draft, writing-review & editing)
  | **Competing interests:** The authors have no competing interests to declare. 
  | **Data and materials availability:** Web of Science search results and article fulltext are not publicly available due to intellectual property restrictions.  Preprocessed analysis data (document-term counts and article metadata) and analysis scripts are available at *[doi]*. 
# bibliography: references.bib, refs-manual.bib
output: 
  # https://github.com/rstudio/rticles/pull/486
  # skeleton: <https://github.com/christopherkenny/rticles/tree/master/inst/rmarkdown/templates/science>
  bookdown::pdf_book:
    base_format: rticles::science_article
    keep_tex: true
    move_figures: false
    draft: true
    number_sections: true
    latex_engine: 'xelatex'
header-includes:
  - \usepackage{lineno}
  - \linenumbers
---

@@

\bibliographystyle{Science}
\bibliography{references.bib, refs-manual.bib}
 -->

>>>>

# acknowledgements: |
#   | Thanks to Emily Merchant and John Jackson for some initial discussions that helped clarify the scope of the project and identify some key resources related to the Pioneer Fund and *Mankind Quarterly*.  Thanks to Anthony Sainez for help retrieving the *Mankind Quarterly* articles.  Thanks to Derek Devnich and James Dooley for their work attempting to secure the APA-published articles.  Thanks to Kevin Bird, John Jackson, and Manuela Fernández Pinto for comments on a draft of this paper. 
#   | **Funding:** EJCL's work on this project was partially supported by UC Merced.  DJH's work on this project was not supported by any specific funding. 
#   | **Author contributions:** DJH (conceptualization, data curation, formal analysis, investigation, methodology, project administration, software, validation, visualization, writing-original draft, writing-review & editing); EJCL (conceptualization, methodology, software, validation, visualization, writing-original draft, writing-review & editing)
#   | **Competing interests:** The authors have no competing interests to declare. 
#   | **Data and materials availability:** Web of Science search results and article fulltext are not publicly available due to intellectual property restrictions.  Preprocessed analysis data (document-term counts and article metadata) and analysis scripts are available at *[doi]*. 
# bibliography: references.bib, refs-manual.bib
output: 
  # https://github.com/rstudio/rticles/pull/486
  # skeleton: <https://github.com/christopherkenny/rticles/tree/master/inst/rmarkdown/templates/science>
  bookdown::pdf_book:
    base_format: rticles::science_article
    keep_tex: true
    move_figures: false
    draft: true
    number_sections: true
    latex_engine: 'xelatex'
header-includes:
  - \usepackage{lineno}
  - \linenumbers
---

@@

| 
| Thanks to Emily Merchant and John Jackson for some initial discussions that helped clarify the scope of the project and identify some key resources related to the Pioneer Fund and *Mankind Quarterly*.  Thanks to Anthony Sainez for help retrieving the *Mankind Quarterly* articles.  Thanks to Derek Devnich and James Dooley for their work attempting to secure the APA-published articles.  Thanks to Kevin Bird, John Jackson, and Manuela Fernández Pinto for comments on a draft of this paper. 
| **Funding:** EJCL's work on this project was partially supported by UC Merced.  DJH's work on this project was not supported by any specific funding. 
| **Author contributions:** DJH (conceptualization, data curation, formal analysis, investigation, methodology, project administration, software, validation, visualization, writing-original draft, writing-review & editing); EJCL (conceptualization, methodology, software, validation, visualization, writing-original draft, writing-review & editing)
| **Competing interests:** The authors have no competing interests to declare. 
| **Data and materials availability:** Web of Science search results and article fulltext are not publicly available due to intellectual property restrictions.  Preprocessed analysis data (document-term counts and article metadata) and analysis scripts are available at *[doi]*.
